JavaScript as an Embedded DSL

### 2012-03-26 papers/ecoop2012/article.tex
grammar

\subsection{CPS and Staging}
Let's write the example from listing~\ref{code:cps_scala} in our DSL. We need to define \code{sleep} to use JavaScript's \code{setTimeout}
\footnote{The \code{setTimeout} function executes asynchronously a function passed as an argument after specified delay.}
as a replacement for the \code{Timer} abstraction.
\begin{lstlisting}
def sleep(delay: Rep[Int]) = shift { k: (Rep[Unit]=>Rep[Unit]) =>
  window.setTimeout(fun(k), delay)
}
\end{lstlisting}

>>>>

\subsection{CPS and Staging}
Let's write the example from listing~\ref{code:cps_scala} in our DSL. We need to define \code{sleep} to use JavaScript's \code{setTimeout}
\footnote{The \code{setTimeout} function asynchronously executes a function passed as an argument after a specified delay.}
as a replacement for the \code{Timer} abstraction.
\begin{lstlisting}
def sleep(delay: Rep[Int]) = shift { k: (Rep[Unit]=>Rep[Unit]) =>
  window.setTimeout(fun(k), delay)
}
\end{lstlisting}
